---
title: "Grossepieper_Nils_Assignment05_R"
author: "Nils Grossepieper"
date: "2023-01-25"
output: html_document
---

(1) Register on github.com in case you have not done this already.

Done.


(2) Initialize a new public repository for this assignment on GitHub.

Connected to the public repository Grossepieper_Nils_Assignment05


(3) For the following exercises of this assignment, follow the standard Git workflow
(i.e., pull the latest version of the project to your local computer, then stage,
commit, and push all the modifications that you make throughout the project). Every
logical programming step should be well documented on GitHub with a meaningful commit
message, so that other people (e.g., your course instructor) can follow and understand
the development history. You can do this either using Shell commands or a Git GUI of your
choice.

Future changes in this script will be commented on git.


(4) In the HTML file that you submit, include the hyperlink to the project repository
(e.g., https://github.com/yourUserName/yourProjectName)

Here is the hyperlink to my git repository:
https://github.com/NilsGrossepieper/Grossepieper_Nils_Assignment05.git


(5) Visit the documentation website for the API provided by ticketmaster.com (see here).
Familiarize yourself with the features and functionalities of the Ticketmaster Discovery
API. Have a particular look at rate limits.

I have had a look at the website ticketmaster.com.
I found the following rate limits:
Limit: 5000 API calls per day
Rate limit: 5 requests per second.
Deep Paging: supports retrieving the 100th item (size * page < 1000)


(6) Whithin the scope of this assignment, you do not have to request your own API key.
Instead retrieve a valid key from the API Explorer. This API key enables you to
perform the GET requests needed throughout this assignment. Even though this API key
is not secret per se (it is publicly visible on the API Explorer website), please
comply to the common secrecy practices discussed in the lecture and the tutorial:
Treat the API key as a secret token. Your API key should neither appear in the code
that you are submitting nor in your public GitHub repository.

```{r}

# Read the script with the API key:
source("C:/Users/gross/OneDrive/Dokumente/data/ticket_master_api_key_script.R")

```


(7) Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). Extract
the content from the response object and inspect the resulting list. Describe what you can see.

```{r, warning = FALSE}

# Import all necessary libraries:
library(httr)
library(tidyverse)
library(magrittr)
library(maps)

```

```{r}
# Search for all venues in Germany (page1) (where countryCode = 'DE')
res_venue_ger <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues/",
                     query = list(apikey = ticket_master_key,
                                  "countryCode" = "DE"))

# Print out the query:
con_venue_ger <- content(res_venue_ger)
con_venue_ger

# The number of results on the main list is 20 but we have some nested lists which all
# have different length. You can find information about the name, the city, the 
# URL or the location of venue. For Germany we can find 238 pages with 20 entries 
# per page.
```


(8) Extract the name, the city, the postalCode and address, as well as the url and the longitude
and latitude of the venues to a data frame.

```{r}
# name
# extract the name information:
name <- map_chr(con_venue_ger$`_embedded`$venues, "name")

# city
# create empty city vector:
city <- c()
# loop over all 20 venues:
for (i in 1:20) {
  # add the cities to the vector
  city <- append(city, con_venue_ger$`_embedded`$venues[[i]]$city$name)
}

# postalCode
# create postal code vector (map_dpl does not work), default to:
postalCode <- as.double(map_chr(con_venue_ger$`_embedded`$venues, "postalCode",
                                .default = "NA"))

# address
# create an empty address vector:
address <- c()
# append values via loop
# if there is no such value create NA:
for (i in 1:20) {
  address <- append(address,
                   ifelse(is.null(con_venue_ger$`_embedded`$venues[[i]]$address$line1),
                          NA, con_venue_ger$`_embedded`$venues[[i]]$address$line1))
}

# url
# extract the url information:
url <- map_chr(con_venue_ger$`_embedded`$venues, "url")

# longitude
# create empty vector longitude-vector:
longitude <- c()
# loop over all 20 venues 
# if the value does not exist -> NA, else append by the specific value
for (i in 1:20) {
  # add values to longitude vector 
  longitude <- append(longitude,
                      ifelse(is.null(con_venue_ger$`_embedded`$venues[[i]]$location$longitude),
                             NA, con_venue_ger$`_embedded`$venues[[i]]$location$longitude))
}
# change the data type to double
longitude <- as.double(longitude)

# latitude
# create empty vector latitude-vector
latitude <- c()
# loop over all 20 venues 
# if the value does not exist -> NA, else append by the specific value
for (i in 1:20) {
  # add name to longitude vector 
  latitude <- append(latitude,
                      ifelse(is.null(con_venue_ger$`_embedded`$venues[[i]]$location$latitude),
                             NA, con_venue_ger$`_embedded`$venues[[i]]$location$latitude))
}
# change the data type to double
latitude <- as.double(latitude)

# create the data frame:
venue_ger <- data.frame(name, city, postalCode, address, url, longitude, latitude)
head(venue_ger)
```


(9) Have a closer look at the list element named page. Did your GET request from exercise (7) return all
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your GET request only yielded the first results page containing the first
20 out of several thousands of venues. Check the API documentation under the section Venue Search.
How can you request the venues from the remaining results pages? Iterate over the results pages and
perform GET requests for all venues in Germany. After each iteration, extract the seven variables name,
city, postalCode, address, url, longitude, and latitude. Join the information in one large
data frame. Print the first 10 rows and the shape of the resulting data frame. The resulting data frame
should look something like this (note that the exact number of search results may have changed since
this document has been last modified):

```{r}

# Create a function that creates the data frame.
create_df <- function(countryCode){
  page <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues/",
                     query = list(apikey = ticket_master_key,
                                  "countryCode" = countryCode))
  Sys.sleep(0.2)
  con_page <- content(page)
  nr_pages <- con_page$page$totalPages
  nr_entries <- con_page$page$size
  
  df_all <- data.frame(name = character(), 
                       city = character(), 
                       postalCode = double(),
                       address = character(), 
                       url = character(), 
                       longitude = double(), 
                       latitude = double())
  
  for (p in 0:(nr_pages - 1)) {
    
    # often the api requests throws out an erro when looping over multiple pages
    # that is why while loop is introduced
    control <- NULL
    while(is.null(control)) {
    
    page <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues/",
                     query = list(apikey = ticket_master_key,
                                  "countryCode" = countryCode,
                                  "page" = p))
    content = content(page)
    
    control <- content$`_embedded`$venues
  }
   
# the last page is usually not full 
# to get the number of elements on the last page this if-statement is created:
if (p == (nr_pages - 1)) {
  nr_entries = con_page$page$totalElements %% nr_entries
}
 
    ## name
name <- map_chr(content$`_embedded`$venues, "name", .default = NA)

## city
# create empty city-vector
city <- c()
# loop over all 20 venues
for (i in 1:nr_entries) {
  # add name to city vector
  city <- append(city, ifelse(is.null(content$`_embedded`$venues[[i]]$city$name),NA,
                              content$`_embedded`$venues[[i]]$city$name))
}


## postal code 
# create posal code vector (map_dbl doesnt work), default to prevent error if value is missing
postalCode <- as.double(map_chr(content$`_embedded`$venues, "postalCode", .default = NA))


## address
# create empty adress vector
address <- c()
# append values via loop
# if there is no such value create NA
for (i in 1:nr_entries) {
  address <- append(address, ifelse(is.null(content$`_embedded`$venues[[i]]$address$line1),
                                    NA, content$`_embedded`$venues[[i]]$address$line1))
}

## url 
# create url vector
url <- map_chr(content$`_embedded`$venues, "url", .default = NA)

## longitude 
# create empty longitude-vector
longitude <- c()
# loop over all 20 venues
# if the value does not exist ->NA, else append by the specific value
for (i in 1:nr_entries) {
  # add name to longitude vector
  longitude <- append(longitude, ifelse(is.null(content$`_embedded`$venues[[i]]$location$longitude),
                                    NA, content$`_embedded`$venues[[i]]$location$longitude))
}
# change datatype to double
longitude <- as.double(longitude)

## latitude
# create empty latitude-vector
latitude <- c()
# loop over all 20 venues
# if the value doesn exist ->NA, else append by the specific value
for (i in 1:nr_entries) {
  # add name to longitude vector
  latitude <- append(latitude, ifelse(is.null(content$`_embedded`$venues[[i]]$location$latitude),
                                    NA, content$`_embedded`$venues[[i]]$location$latitude))
}
# change datatype to double
latitude <- as.double(latitude)
print(p)
# create dataframe
df_page <- data.frame(name, city, postalCode,address, url, longitude, latitude)

df_all <- rbind(df_all, df_page)
#print("hello world 2")
#
Sys.sleep(0.2)

  }
  
  return(df_all)
}

german_df <- create_df("DE")

# We you run the code you can see that the code interrupt always a tdifferent points
# sometimes around page 100 but sometime around page 40 or 80 (always after a different
# time). we assume that the website kicks us out.

head(german_df, 10)
dim(german_df)

```

(10) Below, you can find code that produces a map of Germany. Add points to the map indicating the
locations of the event venues across Germany.

```{r}

# based on the code that is mentioned in the assignment 
ggplot(german_df) +
borders("world", "Germany", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4) +
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size = 8, face = 'bold'),
plot.caption = element_text(face = "italic"))

# The visualization is not very practical, since Germany can not bee seen very 
# well. In addition we have some points which are clearly located outside of 
# Germany.
```


(11) You will find that some coordinates lie way beyond the German borders and can be assumed to be faulty.
Set coordinate values to NA where the value of longitude is outside the range (5.866, 15.042) or
where the value of latitude is outside the range (47.270, 55.059) (these coordinate ranges have
been derived from the extreme points of Germany as listed on Wikipedia (see here). For extreme points
of other countries, see here).

```{r}
# create NAs for latitude / longitude if  outside from Germany
# write a function to make life easier for the next tasks

adapt_long_lat <- function(df_country,long_lower,long_upper,lat_lower,lat_upper){
  df_country$longitude <- ifelse(df_country$longitude < long_lower, NA, df_country$longitude)
  
  df_country$longitude <- ifelse(df_country$longitude > long_upper, NA, df_country$longitude)
  
  df_country$latitude <- ifelse(df_country$latitude < lat_lower, NA, df_country$latitude)
  
  df_country$latitude <- ifelse(df_country$latitude > lat_upper, NA, df_country$latitude)
  
  return(df_country)
}

# Longitude is out of the range (5.866, 15.042) or where the value of latitude is
# outside the range (47.270, 55.059)
venue_de_adjust <- adapt_long_lat(german_df, 5.866, 15.042, 47.270, 55.059)

# visualize venues with new
# based on the code that is mentioned in the assignment 
ggplot(venue_de_adjust) +
borders("world", "Germany", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4) +
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size = 8, face = 'bold'),
plot.caption = element_text(face = "italic"))

# The new data frame gives you a much better format where you can see all points
# very clear. Only some points are still located outside of Germany.
``` 


(12) Repeat exercises (9)–(11) for another European country of your choice. (Hint: Clean code pays off! If
you have coded the exercises efficiently, only very few adaptions need to be made.)

```{r}
# I will do the exercises 9 to 11 with the country Czech Republic and its country 
# code 'CZ'

# Exercise 9
czech_df <- create_df("CZ")
head(czech_df, 10)
dim(czech_df)

```
```{r}
# Exercise 10

# based on the code that is mentioned in the assignment 
ggplot(czech_df) +
borders("world", "Czech Republic", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4) +
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Czech Republic",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size = 8, face = 'bold'),
plot.caption = element_text(face = "italic"))

# The visualization is not very practical, since the Czech Republic can not bee
# seen very  well. In addition we have some points which are clearly located outside of 
# the Czech Republic.
```
```{r}
# Exercise 11

# Longitude is out of the range (5.866, 15.042) or where the value of latitude is
# outside the range (47.270, 55.059)
venue_de_adjust <- adapt_long_lat(czech_df, 12.053, 18.513, 48.331, 51.032)

# visualize venues with new
# based on the code that is mentioned in the assignment 
ggplot(venue_de_adjust) +
borders("world", "Czech Republic", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4) +
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Czech Republic",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size = 8, face = 'bold'),
plot.caption = element_text(face = "italic"))

# The new data frame gives you a much better format where you can see all points
# very clear. Only some points are still located outside of the Czech Republic.
``` 